Unsupervised Acquisition of Comprehensive Multiword Lexicons \\ using Competition in an $n$-gram Lattice

### 2017-05-30 tacl.tex
p-value

 \end{tabular}
 \caption{Results of FS identification in various test sets: Countrank = ranking with frequency; PMIrank = PMI-based ranking; minLPRrank = ranking with minLPR; LPRseg = the method of Brooke et \al (2015); ``$-$cl'' = no clearing; ``$-$ovr'' = no penalization of overlaps; ``P'' = Precision; ``R'' = Recall; and ``F'' = F-score. Bold is best in a given column. For ICWSM only, F-score difference relative to best baseline is significant at $p < 0.05$; the difference for all test sets together is significant at $ p < 0.01$; all $p$ values based on the permutation test (Yeh, 2000).}
	 \label{tab:main}

>>>>

 \end{tabular}
 \caption{Results of FS identification in various test sets: Countrank = ranking with frequency; PMIrank = PMI-based ranking; minLPRrank = ranking with minLPR; LPRseg = the method of Brooke et \al (2015); ``$-$cl'' = no clearing; ``$-$ovr'' = no penalization of overlaps; ``P'' = Precision; ``R'' = Recall; and ``F'' = F-score. Bold is best in a given column. For ICWSM only, F-score difference relative to best baseline is significant at $p < 0.05$; the difference for all test sets together is significant at $ p < 0.01$; all p-values based on the permutation test (Yeh, 2000).}
	 \label{tab:main}
